### 2024-11-30 04_T-reX_manuscript-review-documents/external/JRC-peer-review/T-reX_manuscript_JRC-submission_response-to-reviewers.md

This sentence has been rephrased in the revised manuscript make the database manipulation process more clear to the reader. "explode" has been replaced with deconstruct. The second sentence of the conclusion now reads *"It deconstructs, manipulates and reconstructs the database to identify and edit waste and material exchanges..."*

##### Reviewer comment:

*“Line 443: it does not seem to me that T-reX ”examines their connections so supply chain risks and potential environmental damage”: T-reX gives simply an overview of waste generated and materials consumed.”*

##### Author response:

Agreed. It was intended to convey that T-reX can aid the user in this examination by facilitating the generation of specific inventories.The final paragraph of the conclusion has been amended to soften this language and be more specific about what T-reX can do.

----
----

On behalf of all of the authors of T-reX, I would like to extend once our gratitude, the review process was very thorough and I think it has resulted in significant improvement to the manuscript.

All the best,

S.C. McDowall

----
----
----
